\documentclass{exam}
%\usepackage{amsmath}
%\usepackage{polynom}
\usepackage{hyperref}

\newcommand{\boxit}[2]{\begin{center}\framebox[1.3\width]{Estimated time {#1} hours  \hfill Worth {#2} Points}\end{center}}

\firstpageheader{Pack 4}{Gathering Activities}{}
\footer{}{}{} \headrule
\begin{document}
\section{Pack Wide}
\begin{itemize}
\item Bow-Stern-Port-Starboard included Man overboard and three in a boat
\item Knot tying relay
\item Balloon tied to leg STOMP!  Lots of set up for a relatively quick game
\item Keepie upie
\item \underline{\href{https://cubscoutideas.com/139/rattlesnake-game/}{Rattle Snake Game}} Kids hold arms in circle and try to get the other to touch the ``rattle snake"
\item Blindfold Soccer One spotter and one kicker.  Only blind kicker can kick.  Must work in pairs.  Switch half way through.
\item Circle jump rope.  Sock on a stick.  Spin rope in center of circle make scouts jump it.
\end{itemize}
\section{Den Sized}
\begin{itemize}
\item Drop a pin in a jar.  Not too complicated but not terribly entertaining.  Max like four kids at a time
\item Knot tying
\begin{itemize}
\item Overhand
\item Square
\item Bowline
\item Two Half Hitches
\item Taut line hitch
\end{itemize}
\item Outdoor Code Puzzle
\item Scout Oath on Popsicle Sticks
\item Coin War Cards
\item Long rope and river, bank, bridge.  Much like Bow-Stern but was enjoyable for 5-10 minutes
\item Frogs and Flies (sit in circle with one in middle, picked kid sticks out tongue.  Middle kid has to guess who did it.  Idea from \href{https://www.boyscouttrail.com/content/game/frogs\_and\_flies-521.asp}{here}
\item Clothespin tag.  Clip the pins and try to steal them.  When you get one, you attach it to yourself.  Idea from \href{https://www.boyscouttrail.com/content/game/clothespin\_tag-1465.asp}{here}
\end{itemize}

\end{document}